\vspace{-2cm} Government websites as data: A methodological pipeline with application to the websites of municipalities in the United States

### 2018-07-29 paper/tables/tabBoilerplateIllustration.tex
updated the boilerplate illustration figures and table to the new weights

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Fri Jul 27 16:07:13 2018
\begin{table}[ht]
\centering
\begingroup\small
\begin{tabular}{lrr}
  \hline
Line & Substantive & Boilerplate \\ 
  \hline
address other than your mailing address where you  & 1.00 & 0.00 \\ 
  unsworn falsification a person commits the crime o & 1.00 & 0.00 \\ 
  such as the subdivision name lot and block highway & 1.00 & 0.00 \\ 
  o if you are registered to vote in anchorage and y & 1.00 & 0.00 \\ 
  absentee ballots are mailed in the order that appl & 1.00 & 0.00 \\ 
  return your ballot as soon as possible voted ballo & 1.00 & 0.00 \\ 
  parks and recreation is committed to providing rea & 1.00 & 0.00 \\ 
  parks and recreation is committed to providing rea & 1.00 & 0.00 \\ 
  this request type is to log track inspections for  & 1.00 & 0.00 \\ 
  chief doll has been with apd since and has served  & 1.00 & 0.00 \\ 
  walker jack & 0.00 & 1.00 \\ 
  jones jewel & 0.00 & 1.00 \\ 
  acda conference room & 0.00 & 1.00 \\ 
  sec ptn of & 0.00 & 1.00 \\ 
  mh property llc & 0.00 & 1.00 \\ 
  friends of pets & 0.00 & 1.00 \\ 
  change of address & 0.00 & 1.00 \\ 
  municipal code mobile & 0.00 & 1.00 \\ 
  register your vehicle & 0.00 & 1.00 \\ 
  contact phone number & 0.00 & 1.00 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Lines (or the first 50 characters of a line) in the corpus of Anchorage, AK, with the 10 highest and lowed probabilities of being classified as boilerplate.} 
\end{table}

>>>>

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Sat Jul 28 20:51:59 2018
\begin{table}[ht]
\centering
\begingroup\small
\begin{tabular}{lrr}
  \hline
Line & Substantive & Boilerplate \\ 
  \hline
have questions & 0.00 & 1.00 \\ 
  stay connected & 0.00 & 1.00 \\ 
  accident or injury & 0.00 & 1.00 \\ 
  fire damaged buildings & 0.00 & 1.00 \\ 
  gas connections & 0.00 & 1.00 \\ 
  harboring of vagrants & 0.00 & 1.00 \\ 
  roof system problem & 0.00 & 1.00 \\ 
  violation plat note & 0.00 & 1.00 \\ 
  violation setback & 0.00 & 1.00 \\ 
  violation site plan & 0.00 & 1.00 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Lines (or the first 50 characters of a line) in the corpus of Anchorage, AK, with the 10 highest probabilities of being classified as boilerplate.} 
\end{table}
